### 2018-09-28 paper.tex
Wip

\setlist[itemize]{
  itemsep=4pt,
  topsep=4pt,
}

@@

\begin{itemize}
\item The Python module \verb|tensorflow| should be installed
\item Additional Python modules required by \verb|tensorflow| should
  also be installed
\item Installed software should work as expected on the target system
\item At a future date \verb|tensorflow| may be similarly uninstalled along
  with its no-longer-needed required packages
\item The act of installing and uninstalling \verb|tensorflow| should
  not break or otherwise destabilize other installed software on the
  target system
\end{itemize}

@@

\begin{lstlisting}[
    caption=Simple Guild file example,
    label={lst:guild-file}]
model: mnist
description:
  Logistic regression classifier
  of MNIST digits
operations:
  train:
    main: train_mnist
    flags:
      batch-size: 32
      train-steps: 1000
  evaluate:
    main: eval_mnist
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Model resource example,
    label={lst:resource}]
model: mnist
resources:
  idx-data:
    description:
      MNIST dataset in compressed
      IDX format
    sources:
      - train-images-idx3-ubyte.gz
      - train-labels-idx1-ubyte.gz
      - t10k-images-idx3-ubyte.gz
      - t10k-labels-idx1-ubyte.gz
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Sample project Guild file,
    label={lst:published-model}]
model: sample
operations:
  prepare-data:
    description:
      Prepare data for training
    main: prepare_data
    requires: raw-data
  train:
    description: Train model
    main: train
    requires: prepared-data
  export-model:
    description:
      Export model for deployment
    main: export_model
    requires: trained-model
resources:
  raw-data:
    description: Raw data for training
    sources:
      - url: http://mydata.com/raw.tgz
  prepare-data:
    description: Prepared data
    sources:
      - operation: prepare-data
  trained-model:
    description: Trained model
    sources:
      - operation: train
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Sample package definition,
    label={lst:package}]
package: sample-project
version: 1.0
description: Sample packaged project
url: https://my.co/packages/sample
author: John Doe
author-email: john@my.co
license: Apache 2.0
requires: [keras, Pillow, matlab]
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Sample Guild file for a pet classifier,
    label={lst:pet-stub}]
model: pets
description:
  Pet classifier using a CNN
operations:
  train:
    description: Train the classifier
    main: train
    flags:
      images:
        description:
          Directory containing the pet
          images to train
        required: yes
      epochs:
        description:
          Number of epochs to train
        default: 100
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Configuration inheritance,
    label={lst:inheritance}]
- config: model-base
  operations:
    train:
      main: train --model {{model-name}}
      flags:
        epochs: 100
        learning-rate: {{default-lr}}

@@

- model: cnn
  extends: model-base
  params:
    model-name: cnn
    default-lr: 0.0001
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Extending PNASNet Mobile,
    label={lst:extend-slim}]
- model: my-classifier
  extends: gpkg.slim.models/pnasnet-mobile
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Shared configuration (e.g. defined in shared.yml),
    label={lst:shared}]
- config: model-base
  operations:
    train: train
\end{lstlisting}

\begin{lstlisting}[
    caption=Use of includes (e.g. defined in guild.yml),
    label={lst:include-shared}]
- include: shared.yml

@@

- model: model-b
  extends: model-base
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Including shared flag configuration,
    label={lst:include-flags}]
- config: default-train-flags
  flags:
    epochs: 100
    batch-size: 32
    learning-rate: 0.01

- model: sample
  operations:
    train:
      main: train
      flags:
        $include: default-train-flags
        learning-rate: 0.001
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Reusing a Python main module,
    label={lst:tflite_convert}]
model: sample
operations:
  tflite:
    main: tensorflow/contrib/lite/python/tflite_convert
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Quickly enabling model deploy,
    label={lst:deploy}]
- package: classifiers
  requires: [server-utils]

- model: resnet-classifier
  operations:
    train: resnet_train
    deploy: server_utils.deploy
    requires: trained-model
  resources:
    trained-model:
      sources:
        - operation: train
\end{lstlisting}

@@

\begin{lstlisting}[
    caption=Model tests,
    label={lst:tests}]
- test: help
  steps:
    - compare-help: test/help
- test: model
  steps:
    - run-op: prepare-samples
      flags:
        images: test/samples
    - run-op: train
      expected:
        - file: checkpoint
    - run-op: evaluate
      expected:
        - scalar: accuracy > 0.7
\end{lstlisting}

@@

Guild AI is primarily a command line tool. Users type Guild AI
commands in the form:

{\footnotesize
\begin{verbatim}
guild COMMAND [ARG]...
\end{verbatim}}

@@

\subsection{History and Lessons Learned}

- Workshops
- User feedback

- slim, object-detection, mnist, hello

\subsection{Early Use}

\section{Summary}

>>>>

\setlist[itemize]{
  itemsep=4pt,
  topsep=4pt,
  labelindent=1em,
  leftmargin=1em,
}

@@

\begin{itemize}
\item The Python module \verb|tensorflow| should be installed.
\item Additional Python modules required by \verb|tensorflow| should
  also be installed.
\item Installed software should work as expected on the target system.
\item At a future date \verb|tensorflow| may be similarly uninstalled
  along with its no-longer-needed required packages.
\item The act of installing and uninstalling \verb|tensorflow| should
  not break or otherwise destabilize other installed software on the
  target system.
\end{itemize}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Simple Guild file example,
    label={lst:guild-file}]
model: mnist
description:
  Logistic regression classifier
  of MNIST digits
operations:
  train:
    main: train_mnist
    flags:
      batch-size: 32
      train-steps: 1000
  evaluate:
    main: eval_mnist
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Model resource example,
    label={lst:resource}]
model: mnist
resources:
  idx-data:
    description:
      MNIST dataset in compressed
      IDX format
    sources:
      - train-images-idx3-ubyte.gz
      - train-labels-idx1-ubyte.gz
      - t10k-images-idx3-ubyte.gz
      - t10k-labels-idx1-ubyte.gz
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Sample project Guild file,
    label={lst:published-model}]
model: sample
operations:
  prepare-data:
    description:
      Prepare data for training
    main: prepare_data
    requires: raw-data
  train:
    description: Train model
    main: train
    requires: prepared-data
  export-model:
    description:
      Export model for deployment
    main: export_model
    requires: trained-model
resources:
  raw-data:
    description: Raw data for training
    sources:
      - url: http://mydata.com/raw.tgz
  prepare-data:
    description: Prepared data
    sources:
      - operation: prepare-data
  trained-model:
    description: Trained model
    sources:
      - operation: train
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Sample package definition,
    label={lst:package}]
package: sample-project
version: 1.0
description: Sample packaged project
url: https://my.co/packages/sample
author: John Doe
author-email: john@my.co
license: Apache 2.0
requires: [keras, Pillow, matlab]
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Sample Guild file for a pet classifier,
    label={lst:pet-stub}]
model: pets
description:
  Pet classifier using a CNN
operations:
  train:
    description: Train the classifier
    main: train
    flags:
      images:
        description:
          Directory containing the pet
          images to train
        required: yes
      epochs:
        description:
          Number of epochs to train
        default: 100
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Configuration inheritance,
    label={lst:inheritance}]
- config: model-base
  operations:
    train:
      main: train --model {{model-name}}
      flags:
        epochs: 100
        learning-rate: {{default-lr}}

@@

- model: cnn
  extends: model-base
  params:
    model-name: cnn
    default-lr: 0.0001
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Extending PNASNet Mobile,
    label={lst:extend-slim}]
- model: my-classifier
  extends: gpkg.slim.models/pnasnet-mobile
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Shared configuration (e.g. defined in shared.yml),
    label={lst:shared}]
- config: model-base
  operations:
    train: train
\end{lstlisting}
\end{figure}

\begin{figure}
\begin{lstlisting}[
    caption=Use of includes (e.g. defined in guild.yml),
    label={lst:include-shared}]
- include: shared.yml

@@

- model: model-b
  extends: model-base
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Including shared flag configuration,
    label={lst:include-flags}]
- config: default-train-flags
  flags:
    epochs: 100
    batch-size: 32
    learning-rate: 0.01

- model: sample
  operations:
    train:
      main: train
      flags:
        $include: default-train-flags
        learning-rate: 0.001
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Reusing a Python main module,
    label={lst:tflite_convert}]
model: sample
operations:
  tflite:
    main: tensorflow/contrib/lite/python/tflite_convert
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Quickly enabling model deploy,
    label={lst:deploy}]
- package: classifiers
  requires: [server-utils]

- model: resnet-classifier
  operations:
    train: resnet_train
    deploy: server_utils.deploy
    requires: trained-model
  resources:
    trained-model:
      sources:
        - operation: train
\end{lstlisting}
\end{figure}

@@

\begin{figure}
\begin{lstlisting}[
    caption=Model tests,
    label={lst:tests}]
- test: help
  steps:
    - compare-help: test/help
- test: model
  steps:
    - run-op: prepare-samples
      flags:
        images: test/samples
    - run-op: train
      expected:
        - file: checkpoint
    - run-op: evaluate
      expected:
        - scalar: accuracy > 0.7
\end{lstlisting}
\end{figure}

@@

Guild AI is primarily a command line tool. Users type Guild AI
commands in the form: \verb|guild COMMAND [ARG]...|

@@

There have been several packaging initiatives that have produced
reusable models (ref) that fulfill the goals outlined in this
paper. Specifically, the packages support:

\begin{itemize}
\item Use without code changes
\item Reuse by developers who want to new models that leverage
  packaged functionality
\item Package maintainer workflow as described in
  Section~\ref{sec:package-maintainer}
\item Regression testing as a part of a continuous integration process
\end{itemize}
